Honey Bees - DESeq

### 2018-09-04 Galbraith/DESeq2/makeDataMetrics.Rmd
Remove old files

    GDC1 <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    GDV1 <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    GD_VIRUS1 <- metrics[which(metrics$padj <0.05),]$ID

    GDV <- unname(sapply(GDV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GDC <- unname(sapply(GDC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GD_VIRUS <- unname(sapply(GD_VIRUS1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

    saveRDS(GDV, file="GDV.Rds")
    saveRDS(GDC, file="GDC.Rds")
    saveRDS(GD_VIRUS, file="GD_VIRUS.Rds")

>>>>

    sigMetrics <- metrics[which(metrics$padj <0.05),]
    GDC1 <- sigMetrics[which(sigMetrics$log2FoldChange>0),]$ID
    GDV1 <- sigMetrics[which(sigMetrics$log2FoldChange<0),]$ID
    GD_TOTAL1 <- metrics[which(metrics$padj <0.05),]$ID

    GDV <- unname(sapply(GDV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GDC <- unname(sapply(GDC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GD_TOTAL <- unname(sapply(GD_TOTAL1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

    saveRDS(GDV, file="GDV.Rds")
    saveRDS(GDC, file="GDC.Rds")
    saveRDS(GD_TOTAL, file="GD_TOTAL.Rds")
